\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
where experts from industry, government, and academia discussed first RDF validation use cases. 
%for RDF data validation and constraint formulation.
In 2014, two working groups on RDF validation have been established: 
the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
with the intention to collaboratively collect case studies, use cases, requirements, and solutions in a comprehensive and structured way \cite{BoschEckert2014}. 
Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
we identified by today 81 constraint types, where each type corresponds to a specific requirement in the database. In a technical report, we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.

Various constraint languages exist or are being developed that support more or less of these constraint types. For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}, and the \emph{Web Ontology Language} \emph{(OWL)}. Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is also very popular to formulate and check constraints \cite{Fuerber2010}. We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.

@@

It turned out that 64\% of the 81 constraint types are actually expressible in DL. Only for the remaining 36\%, other means, i.e., other constraining elements, had to be identified. This is not surprising if we consider that OWL is based on Description Logics. When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique naming assumption (nUNA). Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.

@@

Complex constraints of frequently used constraint types which correspond to DL axioms like \emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity} can also be simplified in form of simple constraints. Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.

@@

\emph{Shape Expressions (ShEx)} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

@@

We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
When language designers extend constraint languages 
to be able to formulate constraints of not yet supported constraint types,
our proposal enables to reuse the validation implementation of these constraint types 
by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
by providing a \emph{SPIN} mapping
for each constraint type\footref{RDF-CV-2-SPIN}  
whose constraints are represented generically \cite{BoschEckert2015-2}. 
Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
leads to exactly the same validation results, 
i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).

>>>>

In 2013, the W3C organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
where experts from industry, government, and academia discussed first RDF validation use cases. 
%for RDF data validation and constraint formulation.
In 2014, two working groups on RDF validation have been established: 
the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}}
with the intention to collaboratively collect case studies, use cases, requirements, and solutions in a comprehensive and structured way \cite{BoschEckert2014}. 
Based on our work in the DCMI and in cooperation with the W3C working group,
we identified by today 81 constraint types, where each type corresponds to a specific requirement in the database. In a technical report, we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.

Various constraint languages exist or are being developed that support more or less of these constraint types. For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}. Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}. We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.

@@

It turned out that 64\% of the 81 constraint types are actually expressible in DL. Only for the remaining 36\%, other means, i.e., other constraining elements, had to be identified. This is not surprising if we consider that OWL is based on Description Logics. When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique name assumption (nUNA). Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.

@@

Complex constraints of frequently used constraint types which correspond to DL axioms like \emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity} can also be simplified in form of simple constraints. Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar.

@@

\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

@@

We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
When language designers extend constraint languages 
to be able to formulate constraints of not yet supported constraint types,
our proposal enables to reuse the validation implementation of these constraint types 
by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
by providing a \emph{SPIN} mapping
for each constraint type\footref{RDF-CV-2-SPIN}  
whose constraints are represented generically. 
Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
leads to exactly the same validation results, 
i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).
